MLCommons Earthquake Science Benchmark

### 2022-02-21 paper-capstone-earthquake.tex
Updates from Overleaf
citations

\PassOptionsToPackage{hyphens}{url}
\documentclass[sigplan,screen]{acmart}
\usepackage{todonotes}
\usepackage{graphicx}
\usepackage{wrapfig}
\usepackage[pdf]{graphviz}
\usepackage{xpatch}
\usepackage{adjustbox}
\usepackage{makecell} 
\usepackage{ifthen}

@@

\acmBooktitle{Woodstock '18:
  ACM Symposium on Neural Gaze Detection, June 03--05, 2018,
  Woodstock, NY}

@@

@@

\TODO{Add your personal computers to this table \url{https://github.com/Data-ScienceHub/mlcommons-science/issues/37}}
\begin{table*}[htb]
    \caption{Overview of compute resources.}
    \label{tab:desktops}
    \centering
%\begin{adjustbox}{angle=90}
\begin{adjustbox}{max width=\textwidth}
    \begin{tabular}{|r|l|l|r|l|l|l|l|l|}
        \hline
        See also & Organization   & Machine                         & Processors    & GPUs             & \makecell{Memory\\/Device} &  \makecell{GPU\\/Device} & \makecell{No. of\\ nodes} & Commissioned \\ 
        \hline
        \hline
         Table \ref{tab:gcompute}   & 
         Gregor    & 
         5950X   &  
         1 &   
         \href{https://www.gigabyte.com/Graphics-Card/GV-N307TGAMING-OC-8GD#kf}{GIGABYTE Gaming RTX 3070TI}  & 
         8GB & 
         1 & 
         1 & 
         Sep 2021   \\
            & 
            & 
            &  
            &   
         \href{https://rog.asus.com/us/graphics-cards/graphics-cards/rog-strix/rog-strix-rtx3090-o24g-gaming-model/}{ASUS ROG Strix RTX 3090} & 
         24GB & 
         1 & 
         1 & 
         Feb 2022   \\
         \hline
         \ref{sec:tcomputer}   & Thomas.A  & i7-8750H &  1 &   NVIDIA GeForce RTX 2070 with Max-Q Design  & 16GB & 1 & 1 & 2019   \\
         \hline
         \ref{sec:t2computer}   & Thomas.B  & i7-7700HQ &  1 &   NVIDIA GeForce GTX 1060  & 16GB & 1 & 1 & 2017   \\
         \hline
    \end{tabular}
    \end{adjustbox}
\end{table*}

@@

\BIOFIG{images/bio/gregor.png}{Robert Knuuti}{is a Graduate Student at
  University of Virginia's School of Data Science. He has over 10
  years experience in system architecture and software engineering,
  and specializes in Development Operations and Cloud Computing. He
  has constructed air gapped Continuous Integration and Continuous
  Delivery systems for multiple organizations each supporting more
  than 100 developers and has facilitated the construction of
  repeatable, tractable builds for users of these systems.}

>>>>

\PassOptionsToPackage{hyphens}{url}
\documentclass[sigplan,screen]{acmart}
\usepackage{todonotes}
\usepackage{graphicx}
\usepackage{wrapfig}
\usepackage[pdf]{graphviz}
\usepackage{xpatch}
\usepackage{adjustbox}
\usepackage{makecell} 
\usepackage{ifthen}
\usepackage{comment}

@@

\acmBooktitle{Report for the MLCommons Science Working Group in collaboration with University of Virginia, May 2022, Charlottesville, VA}

@@

\begin{comment}
\parindent 0pt {\bf Citation:}

\begin{footnotesize}
\begin{verbatim}@TechReport{mlcommons-eartquake,
  author = 	 {Thomas Butler and Robert Knuuti and
              Jake Kolessar and Geoffrey C. Fox and
              Gregor von Laszewski and Judy Fox},
  title = 	 {MLCommons Earthquake Science Benchmark},
  institution =  {MLCommons Science Working Group},
  year = 	 2022,
  type = 	 {Report by University of Virginia},
  address = 	 {Charlottesville, VA},
  month = 	 may,
  note = 	 {The order of the authors and url location may change},
  annote = 	 {Version: draft},
  url = {https://github.com/cyberaide/paper-capstone-mlcommons}
}\end{verbatim}
\end{footnotesize}
\end{comment}

@@

\TODO{Add your personal computers to this table \url{https://github.com/Data-ScienceHub/mlcommons-science/issues/37}}
\begin{table*}[htb]
    \caption{Overview of compute resources.}
    \label{tab:desktops}
    \centering
%\begin{adjustbox}{angle=90}
\begin{adjustbox}{max width=\textwidth}
    \begin{tabular}{|r|l|l|r|l|l|l|l|l|}
        \hline
        See also & Organization   & Machine                         & Processors    & GPUs             & \makecell{Memory\\/Device} &  \makecell{GPU\\/Device} & \makecell{No. of\\ nodes} & Commissioned \\ 
        \hline
        \hline
         Table \ref{tab:gcompute}   & 
         Gregor    & 
         5950X   &  
         1 &   
         \href{https://www.gigabyte.com/Graphics-Card/GV-N307TGAMING-OC-8GD#kf}{GIGABYTE Gaming RTX 3070TI}  & 
         8GB & 
         1 & 
         1 & 
         Sep 2021   \\
            & 
            & 
            &  
            &   
         \href{https://rog.asus.com/us/graphics-cards/graphics-cards/rog-strix/rog-strix-rtx3090-o24g-gaming-model/}{ASUS ROG Strix RTX 3090} & 
         24GB & 
         1 & 
         1 & 
         Feb 2022   \\
         \hline
         \ref{sec:tcomputer}   & Thomas.A  & i7-8750H &  1 &   NVIDIA GeForce RTX 2070 with Max-Q Design  & 16GB & 1 & 1 & 2019   \\
         \hline
         \ref{sec:t2computer}   & Thomas.B  & i7-7700HQ &  1 &   NVIDIA GeForce GTX 1060  & 16GB & 1 & 1 & 2017   \\
         \hline
         Table \ref{tab:rcompute} & Rob.K & AMD Ryzen 9 5900HX & 1 &  NVidia RTX 3080 &  16GB & 1 & 1 & 11/25/2021 \\
         \hline
    \end{tabular}
    \end{adjustbox}
\end{table*}

@@

\BIOFIG{images/bio/rob.png}{Robert Knuuti}{is a Graduate Student at
  University of Virginia's School of Data Science. He has over 10
  years experience in system architecture and software engineering,
  and specializes in Development Operations and Cloud Computing. He
  has constructed air gapped Continuous Integration and Continuous
  Delivery systems for multiple organizations each supporting more
  than 100 developers and has facilitated the construction of
  repeatable, tractable builds for users of these systems.}
